\let\negmedspace\undefined
\let\negthickspace\undefined
\documentclass[journal]{IEEEtran}
\usepackage[a5paper, margin=10mm, onecolumn]{geometry}
\usepackage{lmodern} % Ensure lmodern is loaded for pdflatex
\usepackage{tfrupee} % Include tfrupee package

\setlength{\headheight}{1cm} % Set the height of the header box
\setlength{\headsep}{0mm}     % Set the distance between the header box and the top of the text

\usepackage{gvv-book}
\usepackage{gvv}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{txfonts}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{gensymb}
\usepackage{comment}
\usepackage[breaklinks=true]{hyperref}
\usepackage{tkz-euclide} 
\usepackage{listings}
% \usepackage{gvv}                                        
\def\inputGnumericTable{}                                 
\usepackage[latin1]{inputenc}                                
\usepackage{color}                                            
\usepackage{array}                                            
\usepackage{longtable}                                       
\usepackage{calc}                                             
\usepackage{multirow}                                         
\usepackage{hhline}                                           
\usepackage{ifthen}                                           
\usepackage{lscape}
\begin{document}

\bibliographystyle{IEEEtran}
\vspace{3cm}

\title{2017-XE-53-65}
\author{EE24BTECH11010 - BALAJI B}
% \maketitle
% \newpage
% \bigskip
{\let\newpage\relax\maketitle}

\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\setlength{\intextsep}{10pt} % Space between text and floats


\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\renewcommand{\thetable}{\theenumi}
\begin{enumerate}
    \item Copper is an $FCC$ metal with lattice parameter of 3.62 \AA . Hall effect measurement shows electron mobility to be $3.2 \times 10^{-3} {m}^2 {V}^{-1}{s}^{-1}$. Electrical resistivity of copper is $1.7 \times 10^{-8}  \Omega {m}$. The average number of free electrons per atom in copper is \rule{2.5cm}{0.5pt}(Charge of an electron: $1.6 \times 10^{-19}$ C) \hfill(2017-XE)
    \item In an ionic solid the cation and the anion have ionic radii as 0.8 \AA \ and 1.6 \AA \ respectively. The maximum coordination number of the cation in the structure will be \hfill(2017-XE)
 \begin{enumerate}
     \begin{multicols}{4}
         \item 3
         \item 4
         \item 6
         \item 8
     \end{multicols}
 \end{enumerate}
\item Which of the following statement(s) is / are true regarding susceptibility of a material
\begin{enumerate}[label=\roman*.]
    \item  Magnetic susceptibility is positive for a diamagnetic material 
    \item  Magnetic susceptibility is negative for a diamagnetic material 
    \item  Magnetic susceptibility is negative for an ferromagnetic material 
    \item Magnetic susceptibility is positive for a paramagnetic material
\end{enumerate}
\hfill(2017-XE)
\begin{enumerate}
    \begin{multicols}{4}
        \item (ii) and (iv)\\
        \item (i) and (iii)\\
        \item (ii) and (iii)\\
        \item (i) and (iv)
    \end{multicols}
\end{enumerate}
\item In the truss shown, a mass $m = 10kg$ is hung from the node J. The magnetic of net force(in Newtons) transferred by the truss 
 EFGHIJ onto the truss JKLMNO at the node J is \rule{2.5cm}{0.6pt} \\\\ Assume acceleration due to gravity $g = 10m/s^2$\hfill(2017-XE)
\input{figs/fig1}
\item A ball moves along a plannar frictionless slot as shown. Which one of the paths shown closely matches the path by the ball after it exits the slot at E \hfill(2017-XE)
\begin{enumerate}
    \begin{multicols}{4}
        \item path $m$
        \item path $n$
        \item path $p$
        \item path $q$
    \end{multicols}
\end{enumerate}
\input{figs/fig2.tex}
\item A rod $EF$ moving in a plane has velocity $V_E$ at $E$ and $V_F$ that are parallel to each other. Which of the following \textbf{CANNOT} be true? \hfill(2017-XE)
\input{figs/fig3.tex}
\begin{enumerate}
    \item Both $V_E$ and $V_F$ are perpendicular to $EF$.
    \item Magnitude of $V_E$ is equal to the magnitude of $V_F$ and the angular velocity of $EF$ is zero.
    \item The velocity $V_E$ is not perpendicular to $EF$ and the angular velocity of $EF$ is nonzero.
    \item Magnitude of $V_E$ is not equal to the magnitude of $V_F$ and the angular velocity of $EF$ is nonzero.
\end{enumerate}
\item The beam shown below carries two external moments. A counterclockwise moment of magnitude $2M$ acts at point $B$ and a clockwise moment of magnitude $M$ acts at the free end, $C$. The beam is fixed at $A$. The shear force at a section close to the fixed end is equal to \hfill(2017-XE)
\input{figs/fig4.tex}
\begin{enumerate}
    \begin{multicols}{4}
        \item $\frac{2M}{L}$
        \item $\frac{M}{L}$
        \item 0
        \item $-\frac{M}{L}$
    \end{multicols}
\end{enumerate}
\item Two pendulums are shown below. \textbf{\textit{Pendulum-A}} carries a bob of mass $m,$ hung using a hinged massless rigid rod of length $L$ whereas \textbf{\textit{Pendulum-B}} carries a bob of mass $4m$ and length $L/4$. The ratio of the natural frequencies of \textbf{\textit{Pendulum-A}} and \textbf{\textit{Pendulum-B}} is given by \hfill(2017-XE)
\input{figs/fig5.tex}
\begin{enumerate}
    \begin{multicols}{4}
        \item 1 : 2
        \item 1 : 1
        \item $\sqrt{2}$ : 1
        \item 2 : 1 
    \end{multicols}
\end{enumerate}
\item A closed thin-walled cylindrical steel pressure vessel of wall thickness $t = 1 \ \text{mm}$ is subjected to internal pressure. The maximum value of pressure $p$ (in kPa) that the wall can withstand based on the maximum shear stress failure theory is given by (Yield strength of steel is $200  MPa$ and mean radius of the cylinder $r = 1 m$).

\hfill(2017-XE)
\begin{enumerate}
    \begin{multicols}{4}
        \item 100
        \item 200
        \item 300
        \item 400
    \end{multicols}
\end{enumerate}
\item The state of stress at a point in a body is represented using components of stresses along $X$ and $Y$ directions as shown. Which one of the following represents the state of the stress along $X^\prime$ and $Y^\prime$ axes?($X^\prime$- axis at $45^\degree$ clockwise with respect to $X$- axis)

\hfill(2017-XE)
\input{figs/fig8.tex}
\begin{enumerate}
    \item \input{figs/fig9}
    \item \input{figs/fig10}
    \item \input{figs/fig11}
    \item \input{figs/fig12}
\end{enumerate}
\item An aluminum specimen with an initial gauge diameter $d_0 = 10mm$ and a gauge length $l_0 = 10mm$ is subjected to tension test. A tensile force $P = 50kN$ is applied at the ends of the specimen as shown resulting in an elongation of $1mm$ in the gauge length. The Poisson's ratio ($\gamma$) of the specimen is \rule{2cm}{0.4pt}\\ \\
Shear modulus of the material $G = 25GPa$. Consider engineering stress-strain conditions. \hfill(2017-XE)
\input{figs/fig6}
\item A rectangular sheet $ABCD$ of dimensions $a$ and $b$ along $X$ and $Y$ directions, respectively, is stretched to a rectangle $AB'C'D'$, as shown. The maximum principal strain ($\varepsilon_1$) and minimum principal strain ($\varepsilon_2$) due to the stretch are given by

\hfill(2017-XE)
\input{figs/fig7}
\begin{enumerate}
    \begin{multicols}{2}
        \item $\varepsilon_1 = 0.001$ and $\varepsilon_2 = 0.001$
        \item $\varepsilon_1 = -0.001$ and $\varepsilon_2 = 0.001$
        \item $\varepsilon_1 = 0.001$ and $\varepsilon_2 = -0.001$
        \item  $\varepsilon_1 = -0.001$ and $\varepsilon_2 = -0.001$
    \end{multicols}
\end{enumerate}
\item A solid bar of uniform square cross-section of side $b$ and length $L$ is rigidly fixed to the supports at the two ends. When the temperature in the rod is increased uniformly by $T$, the bar undergoes elastic buckling. Assume Young's modulus $E$ and coefficient of thermal expansion $\alpha$ to be independent of temperature. The coefficient of thermal expansion $\alpha$ is given by \hfill(2017-XE)
\begin{enumerate}
    \begin{multicols}{4}
        \item $\frac{3\pi^2b^2}{T_cL^2}$
         \item $\frac{\pi^2b^2}{T_cL^2}$
          \item $\frac{\pi^2b^2}{2T_cL^2}$
           \item $\frac{\pi^2b^2}{3T_cL^2}$
    \end{multicols}
\end{enumerate}
\end{enumerate}
\end{document}